\documentclass[12pt]{report}
\usepackage{amssymb}
\usepackage{amsmath}

\usepackage{multicol}
\usepackage{graphicx}
\usepackage{subfigure}
\usepackage{verbatim}

%\usepackage{adjustbox}

\usepackage[letterpaper,left=1cm,right=2cm, top=1.5cm,
bottom=1.5cm,head=0cm,foot=1cm]{geometry}

\parindent=0in


\newcommand{\m}{\mbox{ m }}
\newcommand{\kg}{\mbox{ kg }}
\newcommand{\s}{\mbox{ s }}
\newcommand{\ke}{\mbox{\small KE}}
\newcommand{\pe}{\mbox{\small PE}}


\newcommand{ \probDir}[1]{{ \bf\small #1 \mbox{  }}}

\newcommand{ \breakList}{\setcounter{saveenum}{\value{enumi}} \end{enumerate}}
\newcommand{ \contList}{\begin{enumerate} \setcounter{enumi}{\value{saveenum}}}

\newcounter{saveenum}

\def \wspace{5cm}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}

{\bf{Honors Physics} \hfill Math of Circles \hfill {Mr. Kelley}} \\ \\
%%%%%%%%%%

\hspace{3cm} \parbox{12cm}{\centering \probDir{Answer the following questions on a separate sheet of paper.  Draw and label diagrams for almost everything.}} \\ \\

Recall that the circumference of a circle of radius $r$ is given by the formula $C=2\pi r$

\begin{enumerate}
\item What is the circumference of a circle of radius 1? \\
\item What is the distance half way around a circle of radius 1? \\
\item If 360$^\circ$ is a full rotation, what fraction of a full rotation is $60^\circ$? \\
\item If a full rotation is $2\pi$, what fraction of a rotation is $3\pi / 4$? \\
\item What is the circumference of a bike tire with a radius measuring 60 cm? \\
\item If the bike tire from before makes a full rotation every 2 seconds, how fast is an ant traveling on the edge of the tire? \\
\item How far does the ant travel in 0.75 seconds? \\
\item What angle (degrees) has the ant swept through in 0.75 seconds? (Hint: Use the previous questions and a proportion) \\
\item What angle (radians) has the ant swept through in 0.75 seconds? \\
\item Convert 35 rpm (rotations per minute) to degrees per second. \\
\item Convert 18$\pi$ radians per second to rpm. \\
\item How fast is an ant traveling on a tire of radius 60 cm rotating at 100$^\circ$ per second? \\
\item How fast is an ant traveling on a tire of radius 80 cm rotating at 100$^\circ$ per second? \\
\item Write, in a few sentences or more, what you have learned from these questions.  Focus on the questions about the ant.  Use the key terms \emph{angular velocity} and \emph{linear velocity}.  (See Ch. 8 in the book)

\end{enumerate}


\vspace{1cm}


\vspace{1.5cm}
\end{document}