\documentclass[12pt]{report}
\usepackage{amssymb}
\usepackage{multicol}
\usepackage{graphicx}
\usepackage{subfigure}
\usepackage{verbatim}
\usepackage[letterpaper,left=1cm,right=2cm, top=1.5cm,
bottom=1.5cm,head=0cm,foot=1cm]{geometry}

\parindent=0in

\newcommand{ \probDir}[1]{{ \bf\small #1 \mbox{  }}}

\newcommand{ \breakList}{\setcounter{saveenum}{\value{enumi}} \end{enumerate}}
\newcommand{ \contList}{\begin{enumerate} \setcounter{enumi}{\value{saveenum}}}

\newcounter{saveenum}

\def \wspace{4cm}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}

{\bf{Honors Physics} \hfill {Quiz 2: Kinematics} \hfill {Mr. Kelley}} \\ \\
%%%%%%%%%%

\begin{multicols}{2}
\begin{enumerate}
\item A vector $\vec{a}$ points with an angle of $45^\circ$ above the horizontal.  If the $x$-component of $\vec{a}$ is 10 units, what is the $y$-component?
\vspace{\wspace}
\item A football is kicked from the ground with an initial velocity of $\vec{v} = 20$ m$/$s, at $60^\circ$ above the horizontal.  With what velocity (magnitude and direction) will the ball hit the ground?
\vspace{\wspace}
\item Consider the same football being kicked.  The kicker notices that $v_y$ of the ball is $+10$m/s when the ball first reaches eye-level.  What is $v_y$ of the ball when it reaches eye-level again?
\vspace{\wspace}
\item Still the same ball; What is $v_y$ when the ball is exactly half way through its flight?
\vspace{\wspace}
\breakList
\end{multicols}

\vspace{\wspace}

%%%%%%%%%%
\probDir{Show all work on the following problems, which refer to the football in problem 2l:}
%%%%%%%%%%
\contList
\item What is the max height of the football?
\vspace{\wspace}
\pagebreak
\item How long does it take the football to get to the max height?
\vspace{\wspace} \vspace{\wspace}
\item What is the time that the football is in the air?
\vspace{\wspace}
\item How far down the field does the football land?
\breakList
\vspace{\wspace}



\end{document}