\documentclass[12pt]{report}
\usepackage{amssymb}
\usepackage{multicol}
\usepackage{graphicx}
\usepackage{subfigure}
\usepackage{verbatim}
\usepackage[letterpaper,left=1cm,right=2cm, top=1.5cm,
bottom=1.5cm,head=0cm,foot=1cm]{geometry}

\parindent=0in

\newcommand{ \probDir}[1]{{ \bf\small #1 \mbox{  }}}

\newcommand{ \breakList}{\setcounter{saveenum}{\value{enumi}} \end{enumerate}}
\newcommand{ \contList}{\begin{enumerate} \setcounter{enumi}{\value{saveenum}}}

\newcounter{saveenum}

\def \wspace{5cm}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}

{\bf{Honors Physics} \hfill {Test: Kinematics} \hfill {Mr. Kelley}} \\ \\
%%%%%%%%%%
$v = \frac{\Delta x}{t}$ \hfill $v_f = v_0 + at$ \hfill $v_f^2 = v_0^2 + 2 a\Delta x$ \hfill $x_f = x_0 + v_0 t + \frac{1}{2}at^2$


\begin{enumerate}
\item A bicyclist is traveling at a speed of 14 mi/h.  How many seconds does it take them to travel \mbox{50 ft?}  (Hint: 5280 ft = 1 mi)
\vfill
\item How far does a rock fall under the influence of gravity in 3 s, if it starts from rest?
\vfill
\item How far does a rock fall under the influence of gravity in 3 s, if it has an initial velocity of 5 m/s downwards?
\vfill
%%%%
\pagebreak
%%%%
\item Mr. Brazil is riding his motorcycle on a level road at 100 km/h.  He horizontally launches off a cliff overlooking the ocean (don't worry, he's experienced).  The water is 100 m below.
\begin{enumerate}
\item How long before the splash?
\vfill
\item How far from the base of the cliff does he land?
\vfill
\end{enumerate}
%%%%
\pagebreak
%%%%
\item Mr. Kelley is riding his motorcycle at 100 km/h.  While changing tracks on his iPod, he doesn't notice the approaching curb (very dangerous, don't do this).  Hitting the curb at full velocity, he launches at $20^\circ$ above the horizontal.
\begin{enumerate}
\item What is the maximum height Mr. Kelley will clear?
\vfill
\item How far from the curb does he land?
\vfill
\item He survived, and wrote this test, and will give you two points for writing the name of any band or musical group you like in the space below.
\vspace{3cm}
\end{enumerate}
%%%%
\pagebreak
%%%%
\item Mr. Brazil is swimming back to shore after his motorcycle stunt.  In still water he can swim \mbox{1.5 m/s}.  He is trying to swim directly east towards the beach, but there is a 1 m/s rip current pulling him south.  He is 60 m away from the beach.
\begin{enumerate}
\item What does Mr. Brazil's velocity (magnitude and direction) look like from up on the cliff?
\vspace{1cm}
\vfill
\item How long does it take him to get to the beach?
\vfill
\item How far south does he end up from where he started?
\vfill

\end{enumerate}
\end{enumerate}




\end{document}